---
title: "Chapter 2: Framing Democracy"
subtitle: "Online Appendix"
---

```{r setup, include=FALSE}
setwd("~/Dropbox/0 MYCOMP/0_Book manuscript/Lexington/klarahan.github.io")
```

Load libraries
```{r}
library(lubridate)
library(ggplot2)
library(dplyr)
library(tidytext)
library(stm)
library(stminsights)
```

Load and process the text data.
```{r}
#load all articles with keyword "democracy"
all_news <- readRDS("data/democracy_news.RDS")

# save legit stopwords, and add some
stopwords <- tibble(
  tokens = stopwords::stopwords("ko", source = "stopwords-iso"),
  lexicon = "stopwords-iso") 
stopwords <- stopwords %>% 
  add_row(tokens = c("들이", "하기", "그것", "때문"), 
          lexicon = "stopwords-iso")

# make tidytext format of the data and remove stopwords 
tidy_news <- all_news %>%
  dplyr::select(tokens, Newspaper, Date, Body, Prezparty) %>% 
  dplyr::mutate(article =  row_number()) %>%
  tidyr::unnest(tokens) %>% 
  dplyr::anti_join(stopwords) 
  # dplyr::filter(tokens != "민주주의") 

# make term-document matrix from the tidytext format (used later for topic models)
news_sparse <- tidy_news %>%
  dplyr::count(article, tokens) %>%
  cast_sparse(article, tokens, n)
```

Load the Korean sentiment lexicon.
```{r emo, echo=FALSE}
# sentiment lexicon source:
# https://sites.google.com/site/datascienceslab/projects/multilingualsentiment
pos <- readr::read_delim("data/positive_words_ko.txt", delim='\t', col_names=c("term")) %>% 
  rename(word = term) %>% 
  tibble::add_column(sentiment = "positive")
neg <- readr::read_delim("data/negative_words_ko.txt", delim='\t', col_names=c("term")) %>% 
  rename(word = term) %>% 
  tibble::add_column(sentiment = "negative")
senti <- bind_rows(pos, neg) 
senti
```

Count the sentiment words.
```{r}
tidy_news <- tidy_news %>% 
  rename(word = tokens)

tidy_news %>%
  inner_join(senti) %>%
  count(word, sort = TRUE) 

senti_news <- tidy_news %>%
  inner_join(senti) %>%
  count(Newspaper, Prezparty, sentiment) %>%
  tidyr::spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

# pdf("neg_news.pdf", width=6, height=2)
ggplot(senti_news, aes(Prezparty, sentiment, fill = Newspaper)) +
  geom_col(show.legend = FALSE) +
  labs(x = "governments from 1990 to 2014") +
  facet_wrap(~Newspaper, ncol = 3, scales = "free_x") +
  scale_fill_grey() +
  theme_bw()
# dev.off()

```

See the top sentiment words.
```{r}
senti_word_counts <- tidy_news %>%
  inner_join(senti) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

senti_word_counts
```

Plot the top sentiment words.
```{r message=TRUE, warning=TRUE}
senti_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() +
  scale_fill_grey() +
  theme_bw()
```

Did negativity increase in specific administrations?
```{r}
senti_news_admin <- tidy_news %>%
  inner_join(senti) %>%
  mutate(admin = case_when(
    Date > "1990-01-01" & Date < "1993-02-24" ~ "1990-1993 Roh TW",
    Date > "1993-02-25" & Date < "1998-02-24" ~ "1993-1998 Kim YS",
    Date > "1998-02-25" & Date < "2003-02-24" ~ "1998-2003 Kim DJ",
    Date > "2003-02-25" & Date < "2008-02-24" ~ "2003-2008 Roh MH",
    Date > "2008-02-25" & Date < "2013-02-24" ~ "2008-2013 Lee MB",
    Date > "2013-02-25" & Date < "2017-03-10" ~ "2013-2014 Park GH"
  )) %>% 
  filter(!is.na(admin)) %>% 
  count(Newspaper, admin, sentiment) %>%
  tidyr::spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

#pdf("neg_admins.pdf", width=6, height=3)
ggplot(senti_news_admin, aes(admin, sentiment, fill = Newspaper)) +
  geom_col(show.legend = FALSE, position = "stack") +
  labs(x = "administrations") +
  facet_wrap(~Newspaper, ncol = 3, scales = "free_y") +
  scale_fill_grey() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
#dev.off()
```

Plot sentiment words as stacked bars by all newspapers.
```{r}
ggplot(senti_news_admin, aes(admin, sentiment, fill = Newspaper)) +
  geom_col(position = "stack") +
  labs(x = "administrations") +
  # facet_wrap(~Newspaper, ncol = 3, scales = "free_x") +
  scale_fill_grey() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Plot the most unique sentiment words (tf-idf).
```{r}
senti_words <- tidy_news %>%
  inner_join(senti) %>%
  mutate(admin = case_when(
    Date > "1990-01-01" & Date < "1993-02-24" ~ "1990-1993 Roh TW",
    Date > "1993-02-25" & Date < "1998-02-24" ~ "1993-1998 Kim YS",
    Date > "1998-02-25" & Date < "2003-02-24" ~ "1998-2003 Kim DJ",
    Date > "2003-02-25" & Date < "2008-02-24" ~ "2003-2008 Roh MH",
    Date > "2008-02-25" & Date < "2013-02-24" ~ "2008-2013 Lee MB",
    Date > "2013-02-25" & Date < "2017-03-10" ~ "2013-2014 Park GH"
  )) %>%
  filter(!is.na(admin)) %>% 
  filter(sentiment == "negative")  

senti_words <- senti_words %>% 
  filter(admin %in% c("2013-2014 Park GH", "1990-1993 Roh TW")) %>%
  filter(Newspaper == "Hankyoreh") %>%
  group_by(admin) %>%
  count(word, sort = TRUE) %>% 
  ungroup() %>%
  bind_tf_idf(word, admin, n) %>% 
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(admin) %>% 
  top_n(20) %>% 
  ungroup() 

senti_words %>% count(admin)

senti_words %>% 
  ggplot(aes(word, tf_idf, fill = admin)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(admin~., ncol = 3, scales = "free") +
  coord_flip() +
  scale_fill_grey() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
# pdf("neg_admins.pdf", width=6, height=3)
# dev.off()
```

Let's look at the general words, aside from the sentiment words, to get a better idea of the corpus.
Create dataframe with total word counts.
```{r}
news_words <- tidy_news %>%
    mutate(admin = case_when(
    Date > "1990-01-01" & Date < "1993-02-24" ~ "1990-1993 Roh TW",
    Date > "1993-02-25" & Date < "1998-02-24" ~ "1993-1998 Kim YS",
    Date > "1998-02-25" & Date < "2003-02-24" ~ "1998-2003 Kim DJ",
    Date > "2003-02-25" & Date < "2008-02-24" ~ "2003-2008 Roh MH",
    Date > "2008-02-25" & Date < "2013-02-24" ~ "2008-2013 Lee MB",
    Date > "2013-02-25" & Date < "2017-03-10" ~ "2013-2014 Park GH"
  )) %>% 
  count(Newspaper, admin, word, sort = TRUE) 

total_words <- news_words %>% 
  group_by(Newspaper, admin) %>% 
  summarize(total = sum(n))

news_words <- left_join(news_words, total_words)
```


Show term freqency ranks.
```{r}
freq_by_rank <- news_words %>% 
  group_by(Newspaper, admin) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)

freq_by_rank
```

Show term freqency ranks for the most negative administrations.
```{r}
news_words %>% 
  filter(Newspaper == "Hankyoreh") %>% 
  filter(admin %in% c("2013-2014 Park GH", "1990-1993 Roh TW")) %>% 
  group_by(Newspaper, admin) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total)  
```

Which are most unique words for each Newspaper? (tf-idf)
```{r}
news_words <- news_words %>%
  bind_tf_idf(word, Newspaper, n)

news_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

Plot most unique words by each newspaper.
```{r}
news_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(Newspaper) %>% 
  top_n(15) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = Newspaper)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(Newspaper~., ncol = 3, scales = "free") +
  coord_flip() +
  scale_fill_grey() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Plot most unique words by each newspaper for the two most negative administrations.
```{r}
news_words %>%
  arrange(desc(tf_idf)) %>%
  filter(admin %in% c("2013-2014 Park GH", "1990-1993 Roh TW")) %>% 
  filter(Newspaper == "Hankyoreh") %>% 
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(Newspaper) %>% 
  top_n(20) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = Newspaper)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(admin~., ncol = 3, scales = "free") +
  coord_flip() +
  scale_fill_grey() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Now let's look at dtructural topic models for emotional frames regarding democracy.
I analyzed a topic model with 12 topics.
```{r stm: find topics, eval=FALSE, include=FALSE}
all_news <- readRDS("data/democracy_news.RDS") #load all articles with keyword "democracy"

# save stopwords, and add some
stopwords <- tibble(
  tokens = stopwords::stopwords("ko", source = "stopwords-iso"),
  lexicon = "stopwords-iso") 
stopwords <- stopwords %>% 
  add_row(tokens = c("들이", "하기", "그것", "때문"), 
          lexicon = "stopwords-iso")

# pass matrix from tidy to stm 
tidy_news <- all_news %>%
  dplyr::select(tokens, Newspaper, Date, Body, Prezparty) %>% 
  dplyr::mutate(article =  row_number()) %>%
  tidyr::unnest(tokens) %>% 
  dplyr::anti_join(stopwords) %>% 
  dplyr::filter(tokens != "민주주의") 
news_sparse <- tidy_news %>%
  dplyr::count(article, tokens) %>%
  cast_sparse(article, tokens, n)
covariates <- tidy_news %>%
  distinct(article, Newspaper, Date, Body, Prezparty) 

covariates$Prezparty <- as.factor(covariates$Prezparty)
startdate <- as.Date("19900101", "%Y%m%d")
covariates$Date2 <- as.Date(covariates$Date, "%Y%m%d")
covariates$Days <- difftime(covariates$Date2, startdate, units="days") %>% 
  as.numeric()

#fit a model
topic_model <- stm(news_sparse, 
                   K = 12, 
                   prevalence = ~ Newspaper +s(Days),
                   data = covariates,
                   verbose = FALSE, 
                   init.type = "Spectral")

saveRDS(topic_model, "data/topic_model.RDS")

#understand the model output
labelTopics(topic_model)
```

```{r}
topic_model <- readRDS("data/topic_model.RDS")

# prepare covariates
covariates <- tidy_news %>%
  distinct(article, Newspaper, Date, Body, Prezparty) 
startdate <- as.Date("19900101", "%Y%m%d")
covariates$Date2 <- as.Date(covariates$Date, "%Y%m%d")
covariates$Days <- difftime(covariates$Date2, startdate, units="days") %>% 
  as.numeric()
```

Show summary output that shows the relative proportions of topics.
```{r}
plot(topic_model, type = "summary")
```

Show more words that help you to label the topics.
```{r fig.width=7, fig.height=9}
plot(topic_model, type = "labels")
```

Make topic labels (these are mine):
```{r echo=FALSE}
topic_labels <- c(
  "1" = "Topic1:\n Ideology and ideals",
  "2" = "Topic2:\n Civil society, education",
  "3" = "Topic3:\n Public opinion, media",
  "4" = "Topic4:\n North Korea",
  "5" = "Topic5:\n Party politics",
  "6" = "Topic6:\n Law and prosecution",
  "7" = "Topic7:\n The U.S.",
  "8" = "Topic8:\n Government",
  "9" = "Topic9:\n Sentimental humanism",
  "10" = "Topic10:\n Int'l democratizations",
  "11" = "Topic11:\n Civic protest",
  "12" = "Topic12:\n Global human values")
topic_labels_simple <- c(
  "1" = "Ideology and ideals",
  "2" = "Civil society, education",
  "3" = "Public opinion, media",
  "4" = "North Korea",
  "5" = "Party politics",
  "6" = "Law and prosecution",
  "7" = "The U.S.",
  "8" = "Government",
  "9" = "Sentimental humanism",
  "10" = "Int'l democratizations",
  "11" = "Civic protest",
  "12" = "Global human values")
topic_labels_simple
```

Look into sample articles.
```{r echo=FALSE, fig.height=8, fig.width=7}
thoughts1 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 1)$docs[[1]] %>% substring(1,65)
thoughts2 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 2)$docs[[1]] %>% substring(1,65)
thoughts3 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 3)$docs[[1]] %>% substring(1,65)
thoughts4 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 4)$docs[[1]] %>% substring(1,65)
thoughts5 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 5)$docs[[1]] %>% substring(1,65)
thoughts6 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 6)$docs[[1]] %>% substring(1,65)
thoughts7 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 7)$docs[[1]] %>% substring(1,65)
thoughts8 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 8)$docs[[1]] %>% substring(1,65)
thoughts9 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 9)$docs[[1]] %>% substring(1,65)
thoughts10 <- findThoughts(topic_model, texts = covariates$Body,
                          n = 2, topics = 10)$docs[[1]] %>% substring(1,65)
thoughts11 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 11)$docs[[1]] %>% substring(1,65)
thoughts12 <- findThoughts(topic_model, texts = covariates$Body, 
                          n = 2, topics = 12)$docs[[1]] %>% substring(1,65)
par(mfrow = c(3, 4),mar = c( .5, .5, 2, .5))
plotQuote(thoughts1, width = 20, main = topic_labels[1]) 
plotQuote(thoughts2, width = 20, main = topic_labels[2])
plotQuote(thoughts3, width = 20, main = topic_labels[3])
plotQuote(thoughts4, width = 20, main = topic_labels[4])
plotQuote(thoughts5, width = 20, main = topic_labels[5])
plotQuote(thoughts6, width = 20, main = topic_labels[6])
plotQuote(thoughts7, width = 20, main = topic_labels[7])
plotQuote(thoughts8, width = 20, main = topic_labels[8])
plotQuote(thoughts9, width = 20, main = topic_labels[9])
plotQuote(thoughts10, width = 20, main = topic_labels[10])
plotQuote(thoughts11, width = 20, main = topic_labels[11])
plotQuote(thoughts12, width = 20, main = topic_labels[12])
```

Compare which topics have a higher importance in which words (the choice of each topic pair is set below).
```{r echo=FALSE, fig.height=8, fig.width=7}
par(mfrow = c(3, 2))
plot(topic_model, type="perspectives", topics=c(2,9), main = paste(topic_labels_simple[2],topic_labels_simple[9],sep = " vs. "))

plot(topic_model, type="perspectives", topics=c(3,10), main = paste(topic_labels_simple[3],topic_labels_simple[10],sep = " vs. "))

plot(topic_model, type="perspectives", topics=c(2,4), main = paste(topic_labels_simple[2],topic_labels_simple[4],sep = " vs. "))

plot(topic_model, type="perspectives", topics=c(4,11), main = paste(topic_labels_simple[4],topic_labels_simple[11],sep = " vs. "))

plot(topic_model, type="perspectives", topics=c(6,11), main = paste(topic_labels_simple[6],topic_labels_simple[11],sep = " vs. "))

plot(topic_model, type="perspectives", topics=c(8,5), main = paste(topic_labels_simple[8],topic_labels_simple[5],sep = " vs. "))
```

Estimate effects with smoothing line
```{r}
# combine estimates for interaction effects
prep_int <- estimateEffect(1:12 ~ Newspaper * s(Days),
                           topic_model, covariates)
```

Plot relationship between newspapers and topic.
```{r}
# pdf("meta_cov.pdf")
par(mar=c(9,9,4,2))
plot(prep_int, covariate = "Newspaper", 
     topics = c(1:12), model = topic_model, 
     method = "difference", cov.value1 = "Chosun", 
     cov.value2 = "Hankyoreh",
     xlab = "More like Hankyoreh ... More like Chosun",
     labeltype = "custom", custom.labels = c("Ideology",
                                             "Civil society, education",
                                             "Public opinion, media",
                                             "North Korea",
                                             "Party politics",
                                             "Law and prosecution",
                                             "The U.S.",
                                             "Government",
                                             "Sentimental humanism",
                                             "Int'l democratizations",
                                             "Civic protest",
                                             "Global human values"))
# dev.off()

# ggsave("plots/meta_cov.png", width = 6, height = 6)
```

Estimate effects model.
```{r echo=TRUE}
# prepare dataframe with the package stm_insights
effects_int <- get_effects(estimates = prep_int,
                           variable = 'Days',
                           type = 'continuous',
                           moderator = 'Newspaper',
                           modval = "Chosun") %>%
  bind_rows(get_effects(estimates = prep_int,
                variable = 'Days',
                type = 'continuous',
                moderator = 'Newspaper',
                modval = "Hankook"),
            get_effects(estimates = prep_int,
                        variable = 'Days',
                        type = 'continuous',
                        moderator = 'Newspaper',
                        modval = "Hankyoreh"))

labels <- c("Chosun" = "Conservative", "Hankyoreh" = "Liberal")

yearseq <- seq(from = ymd("19900101"),
               to = ymd("20141230"), by = "year")
yearnames <- year(yearseq)
```

Plot topic prevalences by time.
```{r}
# plot interaction effects
# pdf("topics_12.pdf", width = 6, height = 5)

effects_int %>% 
 mutate(label = case_when(
   topic == 1 ~ "Ideology",
   topic == 2 ~ "Civil society, education",
   topic == 3 ~ "Public opinion, media",
   topic == 4 ~ "North Korea",
   topic == 5 ~ "Party politics",
   topic == 6 ~ "Law and prosecution", 
   topic == 7 ~ "The U.S.",
   topic == 8 ~ "Government",
   topic == 9 ~ "Sentimental humanism",
   topic == 10 ~ "Int'l democratizations",
   topic == 11 ~ "Civic protest",
   topic == 12 ~ "Global human values"
 )) %>% 
 # filter(topic == c(1,2,4,6,9,11)) %>%
 filter(moderator != "Hankook") %>% 
 mutate(value = as.Date(value, origin = '1990-01-01')) %>%   
 mutate(moderator = as.factor(moderator)) %>%
 ggplot(aes(x = value, y = proportion, color = moderator,
 group = moderator, fill = moderator)) +
 geom_line() +
 geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2)  +
 theme_minimal() + 
 labs(x = 'Year', y = 'Topic Proportion',
      # title = "Frame: Ideology and ideals",
      color = 'Newspaper', group = 'Newspaper', fill = 'Newspaper') +
 # scale_x_date(date_breaks = "3 years", date_labels = "%Y") +
 # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
 facet_wrap(~label, ncol = 3) +
 scale_fill_grey() +
 scale_colour_grey()

# dev.off()

```

Plot only selected topic prevalences by time.
```{r}
# plot interaction effects
# pdf("topics_6.pdf", width = 6, height = 3)

effects_int %>% 
 mutate(label = case_when(
   topic == 1 ~ "Ideology",
   topic == 2 ~ "Civil society, education",
   topic == 3 ~ "Public opinion, media",
   topic == 4 ~ "North Korea",
   topic == 5 ~ "Party politics",
   topic == 6 ~ "Law and prosecution", 
   topic == 7 ~ "The U.S.",
   topic == 8 ~ "Government",
   topic == 9 ~ "Sentimental humanism",
   topic == 10 ~ "Int'l democratizations",
   topic == 11 ~ "Civic protest",
   topic == 12 ~ "Global human values"
 )) %>% 
 filter(topic == c(11,1,6,5,9,2)) %>%
 filter(moderator != "Hankook") %>% 
 mutate(value = as.Date(value, origin = '1990-01-01')) %>%   
 mutate(moderator = as.factor(moderator)) %>%
 ggplot(aes(x = value, y = proportion, color = moderator,
 group = moderator, fill = moderator)) +
 geom_line() +
 geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2)  +
 theme_minimal() + 
 labs(x = 'Year (1990-2014)', y = 'Topic Proportion',
      # title = "Frame: Ideology and ideals",
      color = 'Newspaper', group = 'Newspaper', fill = 'Newspaper') +
 # scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
 # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
 facet_wrap(~label, ncol = 3) +
 scale_fill_grey() +
 scale_colour_grey()

# dev.off()
```

Estimate effects without smoothing lines.
```{r}
prep_point <- estimateEffect(1:12 ~ Newspaper * Days,
                           topic_model, covariates)
```

Plot relationship between newspapers and topics, but this time I sorted the topics manually by order.
```{r}
# pdf("meta_cov_linear.pdf", width = 6, height = 5)
par(mar=c(4,7,1,1))
plot(prep_point, covariate = "Newspaper", 
     topics = c(11,1,6,3,9,2,5,12,10,8,4,7), 
     model = topic_model, 
     method = "difference", cov.value1 = "Chosun", 
     cov.value2 = "Hankyoreh",
     xlab = "More like Hankyoreh ... More like Chosun",
     labeltype = "custom", custom.labels = c("Civic protest",
                                             "Ideology",
                                             "Law and prosecution",
                                             "Public opinion, media",
                                             "Sentimental humanism",
                                             "Civil society, education",
                                             "Party politics",
                                             "Global human values",
                                             "Int'l democratizations",
                                             "Government",
                                             "North Korea",
                                             "The U.S."
                                             ))
# dev.off()
```

Plot topic prevalences by time, without smoothing lines.
```{r}
# prepare dataframe with the package stm_insights
effects_point <- get_effects(estimates = prep_point,
                           variable = 'Days',
                           type = 'continuous',
                           moderator = 'Newspaper',
                           modval = "Chosun") %>%
  bind_rows(get_effects(estimates = prep_point,
                        variable = 'Days',
                        type = 'continuous',
                        moderator = 'Newspaper',
                        modval = "Hankyoreh"))

labels <- c("Chosun" = "Conservative", "Hankyoreh" = "Liberal")

yearseq <- seq(from = ymd("19900101"),
               to = ymd("20141230"), by = "year")
yearnames <- year(yearseq)

effects_point %>% 
 mutate(label = case_when(
   topic == 1 ~ "Ideology",
   topic == 2 ~ "Civil society, education",
   topic == 3 ~ "Public opinion, media",
   topic == 4 ~ "North Korea",
   topic == 5 ~ "Party politics",
   topic == 6 ~ "Law and prosecution", 
   topic == 7 ~ "The U.S.",
   topic == 8 ~ "Government",
   topic == 9 ~ "Sentimental humanism",
   topic == 10 ~ "Int'l democratizations",
   topic == 11 ~ "Civic protest",
   topic == 12 ~ "Global human values"
 )) %>% 
 # filter(topic == c(1,2,4,6,9,11)) %>%
 filter(moderator != "Hankook") %>% 
 mutate(value = as.Date(value, origin = '1990-01-01')) %>%   
 mutate(moderator = as.factor(moderator)) %>%
 ggplot(aes(x = value, y = proportion, color = moderator,
 group = moderator, fill = moderator)) +
 geom_line() +
 geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2)  +
 theme_minimal() + 
 labs(x = 'Year', y = 'Topic Proportion',
      # title = "Frame: Ideology and ideals",
      color = 'Newspaper', group = 'Newspaper', fill = 'Newspaper') +
 # scale_x_date(date_breaks = "3 years", date_labels = "%Y") +
 # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
 facet_wrap(~label, ncol = 3) +
 scale_fill_grey() +
 scale_colour_grey()
```

