---
  title: "Chapter 6: Framing Welfare"
  subtitle: "Online Appendix"
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(cache = TRUE)
setwd("~/Public/klarahan.github.io")
#Sys.setlocale(locale = "Korean")
```

Load libraries
```{r message=FALSE, warning=FALSE}
library(lubridate)
library(ggplot2)
library(dplyr)
library(tidytext)
library(quanteda)
library(scales)
library(LSX)

```

Load the data.
```{r}
data_wel <- readRDS("data/data_wel_nouns_sample")
```

#Sentiment lexicon
Load the Korean sentiment lexicon.
```{r, echo=FALSE}
Sys.setlocale("LC_ALL", "ko_KR.UTF8")
# sentiment lexicon source:
# https://sites.google.com/site/datascienceslab/projects/multilingualsentiment
pos <- readr::read_delim("data/positive_words_ko.txt", delim='\t', col_names=c("term")) %>% 
  rename(word = term) %>% 
  tibble::add_column(sentiment = "positive")
neg <- readr::read_delim("data/negative_words_ko.txt", delim='\t', col_names=c("term")) %>% 
  rename(word = term) %>% 
  tibble::add_column(sentiment = "negative")
senti <- bind_rows(pos, neg) 
senti
```

See the top sentiment words.
```{r}
tidy_news <- data_wel %>% 
  unnest_tokens(word, text)

tidy_news %>%
  inner_join(senti) %>%
  count(word, sort = TRUE) 

senti_news <- tidy_news %>%
  inner_join(senti) %>%
  count(Newspaper, Prezparty, sentiment) %>%
  tidyr::spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

senti_word_counts <- tidy_news %>%
  inner_join(senti) %>%   
  filter(Government == "1990-1993 Roh TW") %>% 
  count(word, sentiment, Government, sort = TRUE) %>%
  ungroup()

senti_word_counts
```

Plot the top sentiment words.
```{r message=TRUE, warning=TRUE}
senti_word_counts %>%
  group_by(sentiment) %>%
  top_n(25) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() +
  scale_fill_grey() +
  theme_bw()
```

# LSS sentiments

```{r}
#Sys.setlocale(locale = "C")
dict_sentiment <- dictionary(list(positive = c("안정", "개선", "강화", "보장", "확보", "참여"),
                                 negative = c("부담", "투쟁", "논란", "포퓰리즘", "반발", "논쟁")))
dict_sentiment
```

```{r}

# tokenize text corpus and remove various features
corp_sent <- data_wel %>% 
  unique() %>% 
  mutate(Body = gsub("</?[^>]+>|▲ 종이신문보기", "", Body)) %>% 
  corpus() %>% 
  corpus_reshape(to =  "sentences")
toks <- corp_sent %>% 
    tokens()

# create a document feature matrix from the tokens object
dfmat <- toks %>% 
    dfm(remove = "") %>% 
    dfm_trim(min_termfreq = 5)
```

```{r}
topfeatures(dfmat, 20)

```

```{r}
seed <- as.seedwords(dict_sentiment)
seed
```

```{r eval=FALSE, include=FALSE}
# identify context words 
context_terms <- char_context(toks, pattern = "*복지*", p = 0.05)

# run LSS model
tmod_lss <- textmodel_lss(dfmat, seeds = seed,
                          terms = context_terms, k = 300)

saveRDS(tmod_lss, "data/tmod_wel")

```

no need to use this chunk if you use the above. this chunk was only necessary due to rmarkdown errors for building the website.
```{r}
tmod_lss <- readRDS("data/tmod_wel")
```

```{r}
head(coef(tmod_lss), 20) # most positive words

```

```{r}
tail(coef(tmod_lss), 20) # most negative words

```

```{r}
textplot_terms(tmod_lss, dict_sentiment[c("negative", "positive")])
# ggsave("plots/6_wel_seeds.jpg", width=8, height= 5, dpi = 300)

```

```{r}
dfmat <- dfm_group(dfmat)
# predict sentiment scores
pred <- as.data.frame(predict(tmod_lss, se.fit = TRUE, newdata = dfmat))
pred$date <- docvars(dfmat, "Date")
pred$Newspaper <- docvars(dfmat, "Newspaper")

```

```{r}
plot(pred$date, pred$fit, col = rgb(0, 0, 0, 0.05), 
     pch = 20, ylim = c(-1, 1),
     ylab = "Threat Intensity")
```

```{r}
pred_sm_chos <- pred %>% 
  filter(Newspaper == "Chosun") %>% 
  smooth_lss(engine = "locfit")
pred_sm_hani <- pred %>% 
  filter(Newspaper == "Hankyoreh") %>% 
  smooth_lss(engine = "locfit")
pred_sm_hankook <- pred %>% 
  filter(Newspaper == "Hankook") %>% 
  smooth_lss(engine = "locfit")

#Sys.setlocale(locale = "Korean")
head(pred_sm_chos)
head(pred_sm_hani)
head(pred_sm_hankook)

```

plot trend 
```{r}
x <- bind_rows("Chosun" = pred_sm_chos, "Hankyoreh" = pred_sm_hani, .id = "Newspaper") %>% 
  mutate(date = as.Date(date, format = "ymd")) %>% 
  mutate(Newspaper = as.factor(Newspaper)) %>% 
  ggplot(aes(date, fit, group = Newspaper, color = Newspaper, fill = Newspaper)) +
  annotate("rect", xmin = as.Date("1998-02-25"), xmax = as.Date("2008-02-2"), 
           ymin = -Inf, ymax = Inf, alpha = 0.2) +
  geom_line() +
  geom_ribbon(aes(ymin = fit + se.fit, ymax = fit - se.fit), alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c("grey20", "grey70")) +
  theme_bw() +
  labs(x = "Year", y = "Negative vs. Positive",
       caption = "1. 2002 South Korean local elections\n2. Seoul City's anti-free lunch referendum initiated by mayor (conservative) over free welfare controversies")  +
  scale_x_date(breaks = "1 year", labels = date_format("%Y"), 
           limits = as.Date(c("1990-01-01", "2014-12-31")), expand = c(0,0)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "top")  +
  scale_fill_manual(values=c("grey20", "grey70")) +
  annotate(geom = "text", x = as.Date("1994-01-01"), y = 0.85, 
           label = "Conservative\ngovernments", hjust = "center") +
  annotate(geom = "text", x = as.Date("2003-01-01"), y = 0.85, 
           label = "Liberal\ngovernments", hjust = "center") +
  annotate(geom = "text", x = as.Date("2012-01-01"), y = 0.85, 
         label = "Conservative\ngovernments", hjust = "center") +
 annotate(geom = "text", x = as.Date("2002-06-13"), y = 0.6, 
       label = "1", hjust = "center", size = 4) +
 annotate(geom = "text", x = as.Date("2011-08-24"), y = 0.6, 
     label = "2", hjust = "center", size = 4) +
  annotate("segment", x = as.Date(c("2002-06-13", "2011-08-24")),
           xend = as.Date(c("2002-06-13", "2011-08-24")), 
           y = - Inf, yend = 0.55, linetype = 3) 

x
# ggsave("plots/6_wel_lss.jpg", width=9, height= 5, dpi = 300)

```
Look up key periods
```{r}
data_wel %>% 
  filter(Date > "2007-1-01" & Date < "2008-01-31") %>%
  mutate(Body = gsub("</?[^>]+>|▲ 종이신문보기", "", Body)) 
```
read news
```{r}
#Sys.setlocale(locale = "Korean")
x <- data_wel %>% 
  filter(Newspaper == "Chosun"  & Date < "2011-06-30" & Date > "2011-01-01") %>%
  mutate(Body = gsub("</?[^>]+>|▲ 종이신문보기", "", Body)) %>% 
  filter(grepl("무료", text)) %>% 
  select(Date, Title, Body, Newspaper)
x
x[21,] %>% write.csv()
```

# Keyness
Load the data.
```{r}
data_wel <- readRDS("data/toks_wel")
```

Prepare and check
```{r}
#Sys.setlocale(locale = "C")

stopwords <- c("그래픽", "지난해", "한겨레", "기사", "기자", "본지", "측은", "작년", 
               "신문", "종이", "우리", "지면", "보도", "생각", "이날", "간의", 
               "조선일보", "블로그", "일자", "지음", "김동섭", "안영진", "일동", 
               "오후", "회원", "애초", "당초", "가운데", "천억", "중인", "회장", 
               "조치", "조처", "경기도", "입장", "임직원", "여명", "부산", "인천", 
               "학회", "대회", "이사", "이사장", "초청", "김창곤", "부천", "개최", 
               "학회", "세미나", "학술", "총회", "총장", "김성현")
# stopwords_wild <- c("경제민주화*")

#first period
data_words <- data_wel %>% 
  tokens_subset(!docvars(data_wel, "Newspaper") == "Hankook" &  
                docvars(data_wel, "Government") == "1998-2003 Kim DJ") %>% 
  tokens_remove(pattern = stopwords, valuetype = "fixed") %>%
  # tokens_remove(pattern = stopwords_wild, valuetype = "glob") %>% 
  dfm()

#Sys.setlocale(locale = "Korean")
tstat_freq <- data_words %>% 
  dfm() %>% 
  textstat_frequency(n = 20)
head(tstat_freq, 40)

#text scaling
result_keyness <- textstat_keyness(data_words, target = docvars(data_words, "Newspaper") == "Chosun") 
textplot_keyness(result_keyness, n = 10, color = c("grey20", "grey80")) 

#different period
data_words2 <- data_wel %>% 
  tokens_subset(!docvars(data_wel, "Newspaper") == "Hankook" &  
                docvars(data_wel, "Government") == "2008-2013 Lee MB") %>% 
  tokens_remove(pattern = stopwords, valuetype = "fixed") %>%
  # tokens_remove(pattern = stopwords_wild, valuetype = "glob") %>% 
  dfm()

#Sys.setlocale(locale = "Korean")
tstat_freq <- data_words %>% 
  dfm() %>% 
  textstat_frequency(n = 20)
head(tstat_freq, 40)

#text scaling
result_keyness2 <- textstat_keyness(data_words2, target = docvars(data_words2, "Newspaper") == "Chosun") 
textplot_keyness(result_keyness2, n = 10, color = c("grey20", "grey80")) 


```
Look up stray words
```{r}
#Sys.setlocale(locale = "C")
x <- data_wel %>% 
  # tokens_subset(docvars(data_wel, "Newspaper") == "Hankyoreh") %>% 
  kwic(pattern = "당초", window = 5, valuetype = "fixed")
# and label
```

```{r message=FALSE, warning=FALSE}
x <- textplot_keyness(result_keyness, n = 10) +
  xlim(-1800, 1100) +
  labs(color = "Newspaper", subtitle = "1998-2003 Kim DJ government (liberal/progressive)",
       caption = "x-axis: chi-squared test for significance of observed versus expected frequency") +
  scale_color_manual(values = c("black", "grey80"), 
                     labels = c("Chosun Ilbo", "Hankyoreh")) +
  annotate("text", x = -20, y = 20, label = "volunteer work", hjust = 1) +
  annotate("text", x = -20, y = 19, label = "elderly", hjust = 1) +
  annotate("text", x = -20, y = 18, label = "host", hjust = 1) +
  annotate("text", x = -20, y = 17, label = "deliver", hjust = 1) +
  annotate("text", x = -20, y = 16, label = "Korea", hjust = 1) +
  annotate("text", x = -20, y = 15, label = "love", hjust = 1) +
  annotate("text", x = -20, y = 14, label = "plot of land", hjust = 1) +
  annotate("text", x = -20, y = 13, label = "wage earner", hjust = 1) +
  annotate("text", x = -20, y = 12, label = "church", hjust = 1) +
  annotate("text", x = -20, y = 11, label = "town hall", hjust = 1) +
  annotate("text", x = 20, y = 10, label = "labor union", hjust = 0) +
  annotate("text", x = 20, y = 9, label = "Minju ('Korean Democracy')", hjust = 0)  +
  annotate("text", x = 20, y = 8, label = "human rights", hjust = 0) +
  annotate("text", x = 20, y = 7, label = "reform", hjust = 0) +
  annotate("text", x = 20, y = 6, label = "pretext", hjust = 0) +
  annotate("text", x = 20, y = 5, label = "childcare", hjust = 0) +
  annotate("text", x = 20, y = 4, label = "John Doe", hjust = 0) +
  annotate("text", x = 20, y = 3, label = "unemployment", hjust = 0)+
  annotate("text", x = 20, y = 2, label = "labor", hjust = 0) +
  annotate("text", x = 20, y = 1, label = "worker", hjust = 0)

x
# ggsave("plots/6_wel_keyness.jpg", width=7, height=4, dpi = 300)

```

```{r message=FALSE, warning=FALSE}
x <- textplot_keyness(result_keyness2, n = 10) +
  xlim(-1800, 1100) +
  labs(color = "Newspaper", subtitle = "2008-2013 Lee MB government (conservative)",
       caption = "x-axis: chi-squared test for significance of observed versus expected frequency") +
  scale_color_manual(values = c("black", "grey80"), 
                     labels = c("Chosun Ilbo", "Hankyoreh")) +
  annotate("text", x = -30, y = 20, label = "elderly", hjust = 1) +
  annotate("text", x = -30, y = 19, label = "volunteer work", hjust = 1) +
  annotate("text", x = -30, y = 18, label = "center", hjust = 1) +
  annotate("text", x = -30, y = 17, label = "donation", hjust = 1) +
  annotate("text", x = -30, y = 16, label = "facility", hjust = 1) +
  annotate("text", x = -30, y = 15, label = "cost-free", hjust = 1) +
  annotate("text", x = -30, y = 14, label = "culture", hjust = 1) +
  annotate("text", x = -30, y = 13, label = "resident", hjust = 1) +
  annotate("text", x = -30, y = 12, label = "gardenery", hjust = 1) +
  annotate("text", x = -30, y = 11, label = "plot of land", hjust = 1) +
  annotate("text", x = 30, y = 10, label = "problem", hjust = 0) +
  annotate("text", x = 30, y = 9, label = "liberalism", hjust = 0)  +
  annotate("text", x = 30, y = 8, label = "democracy", hjust = 0) +
  annotate("text", x = 30, y = 7, label = "policy", hjust = 0) +
  annotate("text", x = 30, y = 6, label = "solidarity", hjust = 0) +
  annotate("text", x = 30, y = 5, label = "progressive", hjust = 0) +
  annotate("text", x = 30, y = 4, label = "Minju ('Korean Democracy')", hjust = 0) +
  annotate("text", x = 30, y = 3, label = "society", hjust = 0)+
  annotate("text", x = 30, y = 2, label = "labor", hjust = 0) +
  annotate("text", x = 30, y = 1, label = "worker", hjust = 0)

x
# ggsave("plots/6_wel_keyness_Lee.jpg", width=7, height=4, dpi = 300)

```

```{r}

```

